Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-05-26 cvx-flats-neurips21/cvx-flats.tex
section 4

We now turn to two main applications of Theorem~\ref{thm:convex-flats-inf-dim}: new lower bounds on the convex consistency dimension of risk measures (\S~\ref{sec:risk-measures}), and the mode and modal interval (\S~\ref{sec:mode-modal-interval}).
In both cases, we build on previous results due to \citet{frongillo2020elicitation} and \citet{dearborn2020indirect} which showed lower bounds with respect to \emph{identifiable} properties;
a property is $d$-identifiable if its level sets are all $d$-flats, as in Figure~\ref{fig:quadrants-simplices} (Q3).
In contrast, properties elicited by convex losses are generally not identifiable, particularly when the loss is non-smooth.
For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats; see Figure~\ref{fig:quadrants-simplices} (Q1).
It therefore might appear that entirely new ideas are needed.
Indeed, both papers above pose developing similar bounds with respect to convex-elicitable properties as a major open question.

@@

The problem of estimating a risk or uncertainty measure of $Y$ has applications in financial regulation~\cite{acerbi2014back-testing,fissler2016expected,campbell2005review}, robust engineering design\raft{add cites from AFOSR or EnvAI}, and algorithmic fairness~\citep{williamson2019fairness}.
For examples of risk measures, one may wish to estimate the upper confidence bound $\E[Y] + \lambda \Var[Y]$, or the Conditional Value at Risk (CVaR) defined below, in either conditional or unconditional contexts.
Uncertainty measures can be unbiased versions of the above, such as the variance, or an entropy or norm of the distribution of $Y$.
Risk and uncertainty measures are typically not elicitable, so this problem falls under Quadrant 4.
\citet{frongillo2020elicitation} give prediction dimension lower bounds for a broad class of risk and uncertainty measures, namely Bayes risks.
As stated above, these bounds are with respect to identifiable properties, and bounds for convex surrogates are left as a major open question.

>>>>

We now turn to two main applications of Theorem~\ref{thm:convex-flats-inf-dim}: new lower bounds on the convex consistency dimension of risk measures (\S~\ref{sec:risk-measures}) and the mode and modal interval (\S~\ref{sec:mode-modal-interval}).
In both cases, we build on previous results due to \citet{frongillo2020elicitation} and \citet{dearborn2020indirect} which showed lower bounds with respect to \emph{identifiable} properties;
a property is $d$-identifiable if its level sets are all $d$-flats, as in Figure~\ref{fig:quadrants-simplices} (Q3).
In contrast, properties elicited by convex losses are generally not identifiable, particularly when the loss is non-smooth.
For example, the properties elicited by hinge loss and the abstain surrogate are not identifiable, as their level sets are not flats; see Figure~\ref{fig:quadrants-simplices} (Q1).
It therefore might appear that entirely new ideas are needed.
Indeed, both papers above pose developing similar bounds with respect to convex-elicitable properties as a major open question.

@@

The problem of estimating a risk or uncertainty measure of $Y$ has applications in financial regulation~\cite{acerbi2014back-testing,fissler2016expected,campbell2005review}, robust engineering design\raft{add cites from AFOSR or EnvAI}, and algorithmic fairness~\citep{williamson2019fairness}.
For examples of risk measures, one may wish to estimate the upper confidence bound $\E[Y] + \lambda \Var[Y]$, or the Conditional Value at Risk (CVaR) defined below, in either conditional or unconditional contexts.
Uncertainty measures can be unbiased versions, such as the variance, or an entropy or norm of the distribution of $Y$.
Risk and uncertainty measures are typically not elicitable, so this problem falls under Quadrant 4.
\citet{frongillo2020elicitation} give prediction dimension lower bounds for a broad class of risk and uncertainty measures, namely Bayes risks.
As stated above, these bounds are with respect to identifiable properties, and bounds for convex surrogates are left as a major open question.
